### 2025-12-08 about/vita.tex
Updated various things

\goodbreak

\sectheader{Published Creative Writing {\rm($*$ indicates nonfiction)}}

\fictioncount=4
\pubbegin F
\starficitem ``Lanterns,'' {\sl The Malahat Review} {\bf 229} (2025), 7--13.
Winner of the 2024 Constance Rooke Creative Nonfiction Prize. Honourable Mention in the Personal Journalism
category of Canada's 2025 National Magazine Awards.
\ficitem ``Senang Diri,'' {\sl Existere} {\bf 42},2 (2023), 17--25.
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online. Reprinted in
{\sl Best Canadian Stories 2025} (Windsor, Ont.: Biblioasis, 2024), 244--253.
Reprinted in {\sl Infusion} (Toronto, Ont.: Dark Helix Press, 2025), 37--47.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

\leftright{\bf Editor-in-Chief}{\bf December 2023 -- present}
\leftright{\sl Ahoy Literary Magazine}{\sl Montr\'eal, QC, Canada}
\smallskip
Founding member and one of two editors-in-chief of
a semiannual print magazine that publishes poetry, prose, and art.
In charge of English short fiction submissions and the overall typesetting. Share duties with the other
editors related to emails, sales, and magazine launches.
\medbreak

>>>>

\goodbreak
\sectheader{Invited Talks}

\begingroup\frenchspacing\parindent=10pt
\thing Block complexity and idempotent Schur multipliers. 7 December 2025, CMS Winter Meeting,
Toronto.
\endgroup

\goodbreak
\sectheader{Published Creative Writing {\rm($*$ indicates nonfiction)}}

\fictioncount=5
\pubbegin F
\ficitem ``Syazwani,'' {\sl The Ex-Puritan} {\bf 71} (2025), online.
\starficitem ``Lanterns,'' {\sl The Malahat Review} {\bf 229} (2025), 7--13.
Winner of the 2024 Constance Rooke Creative Nonfiction Prize. Honourable Mention in the Personal Journalism
category of Canada's 2025 National Magazine Awards.
\ficitem ``Senang Diri,'' {\sl Existere} {\bf 42},2 (2023), 17--25.
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online. Reprinted in
{\sl Best Canadian Stories 2025} (Windsor, Ont.: Biblioasis, 2024), 244--253.
Reprinted in {\sl Infusion} (Toronto, Ont.: Dark Helix Press, 2025), 37--47.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

\leftright{\bf Editor-in-Chief}{\bf December 2023 -- present}
\leftright{\sl Ahoy Literary Magazine}{\sl Montr\'eal, QC, Canada}
\smallskip
Founding member and one of two directors of a non-profit organization
that publishes poetry, prose, and art in a semiannual print magazine.
In charge of English short fiction submissions as well as the overall typesetting.
Share duties with other editors related to emails, sales, and magazine launches.
\medbreak
